---
title       : Slidify Project 
subtitle    : ggplot example 
author      : petcho
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft}
knit        : slidify::knit2slides
---

## The data Set 

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).


Here is a data sample: 

```{r echo=FALSE}
head(mtcars)
```

--- 

## Functionality
The application uses the ggplot2 library.

* Choose Y-axis and X-axis variables

* Choose a group attribute (group by color)

* Add a regression line

* Automatic update plot title 

---

## ggplot2 example

```{r fig.width=8, fig.height=4}
require(ggplot2)
ggplot(mtcars, aes(x=mtcars$wt, y=mtcars$mpg, colour=factor(mtcars$cyl)))+geom_point() +  geom_smooth(method=lm) +  ggtitle("disp vs cyl") +  xlab("Weight (lb/100)")+  ylab("Miles per Gallon")
```

---

## Shiny Application

the shiny application can be found here 

https://petchon.shinyapps.io/DEVDP/

thank you!

